---
title: "Academic Posters"
subtitle: "Sharing complex research"
author: "Austin Hart, Ph.D."
date: "American University"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: 
      - default
      - css/nhsr.css
      - css/nhsr-fonts.css
    seal: false
    nature:
      highlightStyle: github
      highlightLines: true
      ratio: "16:9"
    includes:
      after_body: [css/insert-logo.html]
---


```{r setup, include = FALSE}
## Libraries
  library(tidyverse)
  library(knitr)
  library(rmdformats)
  library(modelsummary)
  library(gt)

## Global options
  knitr::opts_chunk$set(
    echo = FALSE, 
    prompt = FALSE,
    tidy = FALSE, 
    comment = NA,
    message = FALSE, 
    warning = FALSE,
    dev = 'CairoSVG',
    fig.align = 'center'
)
  
  xaringanExtra::use_panelset()
  options(modelsummary_factory_default = "gt")
```

class: title-slide, left, bottom

# `r rmarkdown::metadata$title`
----
## **`r rmarkdown::metadata$subtitle`**
### `r rmarkdown::metadata$author`
### `r rmarkdown::metadata$date`


---
# Academic posters
### Complex research in a static but engaging format

- Commonly used at:

  - Conferences  

  - Exhibitions

  - Seminars
  
- Primary functions:

  - Stimulate interest in your research
  
  - Present complex findings **succinctly**
  
  - Facilitate networking, engage peers and experts
  

---
class: inverse, middle, center

# Poster $\neq$ paper
## It's a whole different thing.


---
# Core elements of a poster

- **Title** <br> Clear and concise, reflecting the poster's content.

- **Abstract** <br> A brief overview of the research question, methodology, and major findings.

- **Background** <br> Contextualizes the research question or central argument.

- **Methods/Data** <br>  Describes how you conducted the study.

- **Results** <br> Visuals and text highlighting key findings.

- **Discussion** <br> Interpretation of results and implications,

- **Acknowledgments** <br> Credits funding, support, and contributions.


---
class: inverse, middle

# Design Principles for Effective Posters

**Clarity** <br> Use clear, easy-to-read fonts and colors that contrast well.

**Simplicity** <br> Keep the layout simple and uncluttered.

**Visual Appeal** <br> Use charts, graphs, images, and bullet points to break up text and convey information visually.

**Consistency** <br> Maintain consistent use of fonts, colors, and headings.

**Accessibility** <br> Ensure the poster is accessible to people with disabilities (e.g., colorblind-friendly palettes).


---
# What about content?

- Focus on Key Messages <br> Highlight the most important findings or ideas.

- Engage the Audience <br> Use questions or intriguing statements to provoke interest.

- Interactive Elements <br> Consider adding QR codes linking to further info or digital copies of the poster or paper.

- Practice Your Pitch <br> Be ready to explain your poster briefly.

---
class: inverse, middle

# Presenting Your Poster

- Prepare a short summary speech (around 2-3 minutes) to introduce your poster.

- Be ready to answer questions and engage in discussions.

- Network: Use your poster as a conversation starter to network with other researchers.


---
# Poster 2.0 with `posterdown`

.panelset[
  .panel[.panel-name[Examples]

  [Example 1](https://pbs.twimg.com/media/D9Qf0JDX4AEXJRd.jpg:large): From the `posterdown` site
  
  [Example 2](https://curtisnedhansen.github.io/ExamplePoster/): From last term
  
  [Example 3](https://tanvidani.github.io/Portfolio-Poster/): From last term

  ]

  
  .panel[.panel-name[Getting started]
  
- Install `posterdown`: `install.packages('posterdown')`

- Start a new poster: `File -> New -> RMarkdown -> From Template -> posterdown_betterland`

- Save, `knit`, and then edit.

  ]

  .panel[.panel-name[`yaml`]
  
.pull-left[

```yaml
---
main_topsize: 0.2 #percent coverage of the poster
main_bottomsize: 0.1
#ESSENTIALS
title: '**A Better Reproducible Poster Title**'
author:
  - name: '**Austin Hart**'
    affil: 1
    main: true
    email: ahart@american.edu
affiliation:
  - num: 1
    address: PGE, American University 
main_findings:
  - "If you cite me I earn more money."
# continues...
```
]

.pull-right[
```yaml
# continued...
primary_colour: "#0063B2FF"
secondary_colour: "#9CC3D5FF"
accent_colour: "#cc0000"
output: 
  posterdown::posterdown_betteport:
    self_contained: true  # MOST IMPORTANT!
    pandoc_args: --mathjax
    number_sections: false
link-citations: true
knit: pagedown::chrome_print # for pdf
```
]

  
  ]
  
  .panel[.panel-name[Setup]
  
As always, you need a setup chunk:

```{r, echo=TRUE, eval=FALSE}
## Packages
  library(tidyverse)
  library(knitr)
  library(modelsummary)
  library(gt)
```

```{r, echo = T, eval = F}
## Options
  knitr::opts_chunk$set(
    echo = FALSE, 
    comment = NA,
    message = FALSE, 
    warning = FALSE,
    fig.align = 'center'
  )
  options(modelsummary_factory_default = "gt")

```
  
  ]
  
  .panel[.panel-name[Body]

Organize like any report. Just write and code. 

Use appropriate (level-1) sections for structure.

Break up text with images: visuals/tables over text.

Use `<br>` for hard column jumps.

`knit` often.
  
  ]
  
  .panel[.panel-name[OLS]
  
Format regression tables with clear names. Highlight key estimates where you can. Or use a coefficient plot.


```{r, echo = T, eval = F}
## Estimates  
  mods = list(
    '(1)' = lm(Sepal.Length ~ Petal.Length + Sepal.Width, iris),
    '(2)' = lm(Sepal.Length ~ Petal.Length + Sepal.Width + Species, iris)
  )

## Table  
  modelsummary(mods, 
    gof_map = 'nobs', statistic = NULL, 
    stars = c('*' = 0.05),
  ) |>
  tab_style(style = cell_fill(color = 'lightblue'),
            locations = cells_body(rows = 1))

## Coefficient plot  
  modelplot(mods, coef_omit = c(-2, -3)) +
  scale_x_continuous(limits = c(0,1))
```

  ]
  
.panel[.panel-name[output]  

.pull-left[
```{r}
## Estimates  
  mods = list(
    '(1)' = lm(Sepal.Length ~ Petal.Length + Sepal.Width, iris),
    '(2)' = lm(Sepal.Length ~ Petal.Length + Sepal.Width + Species, iris)
  )

## Table  
  modelsummary(mods, fmt = fmt_significant(2), 
    gof_map = 'nobs', statistic = NULL,
    stars = c('*' = 0.05), title = 'DV: Sepal Length',
    coef_map = c(
      'Petal.Length' = 'Petal length',
      'Sepal.Width' = 'Sepal width',
      'Speciesversicolor' = 'Versicolor',
      'Speciesvirginica' = 'Virginica',
      '(Intercept)' = '(Intercept)'
    )
  ) |>
  tab_style(style = cell_text(color = 'red'),
            locations = cells_body(rows = 1)) 
    
```
]
.pull-right[
```{r, fig.dim=c(4,4)}
## plot
  modelplot(mods, coef_omit = c(-2, -3)) +
  scale_x_continuous(limits = c(0,1)) +
  labs(x = 'OLS estimate') +
  theme_classic(base_size = 12) + coord_flip()
    
```
]
]
]